A Greedy Framework for First-Order Optimization

### 2013-12-04 nips/paper.tex
adding slides

\paragraph{Related work.}
A generalized Frank-Wolfe algorithm has also been proposed in \cite{Mairal:2013}, 
which considers first-order convex surrogate functions more generally. Algorithm 3 
of \cite{Mairal:2013} turns out to be equivalent to a line-search formulation of the 
algorithm we propose in this paper. However, the perspective is quite different. 
While both algorithms share the intuition of trying to construct a ``proximal Frank-Wolfe'' 
algorithm, the general framework of \cite{Mairal:2013} studies convex \emph{upper bounds}, 
rather than the convex \emph{lower bounds} of this paper (although for the 
``proximal gradient surrogates'' that they suggest using, their Frank-Wolfe algorithm 
does indeed deal with lower bounds). Another difference is that their analysis focuses 
on the Lipschitz properties of the objective function, whereas we use the more general 
notion of strong convexity with respect to an arbitrary norm. We believe that this 
geometric perspective is useful for tailoring the proximal function to specific applications, 
as demonstrated in our discussion of $q$-herding below. Finally, the saddle point 
perspective on Frank-Wolfe is not present in \cite{Mairal:2013}, although they 
do discuss the general idea of saddle-point methods in relation to convex surrogates.

@@

\paragraph{Acknowledgements.}
Thanks to Cameron Freer, Simon Lacoste-Julien, Martin Jaggi, Percy Liang, Arun Chaganty, and Sida Wang 
for helpful discussions. Thanks also to the anonymous reviewer for suggesting improvements 
to the paper. JR was supported by the Hertz Foundation. JHH was supported by the U.S. Government under FA9550-11-C-0028 and awarded by the Department of Defense, Air Force Office of Scientific Research, National Defense Science and Engineering Graduate (NDSEG) Fellowship, 32 CFR 168a.
fellowship.

>>>>

\paragraph{Related work.}
A generalized Frank-Wolfe algorithm has also been proposed in \cite{Mairal:2013}, 
which considers first-order convex surrogate functions more generally. Algorithm 3 
of \cite{Mairal:2013} turns out to be equivalent to a line-search formulation of the 
algorithm we propose in this paper. However, the perspective is quite different. 
While both algorithms share the intuition of trying to construct a ``proximal Frank-Wolfe'' 
algorithm, the general framework of \cite{Mairal:2013} studies convex \emph{upper bounds}, 
rather than the convex \emph{lower bounds} of this paper (although for the 
``proximal gradient surrogates'' that they suggest using, their Frank-Wolfe algorithm 
does implicitly use lower bounds). Another difference is that their analysis focuses 
on the Lipschitz properties of the objective function, whereas we use the more general 
notion of strong convexity with respect to an arbitrary norm. We believe that this 
geometric perspective is useful for tailoring the proximal function to specific applications, 
as demonstrated in our discussion of $q$-herding below. Finally, the saddle point 
perspective on Frank-Wolfe is not present in \cite{Mairal:2013}, although they 
do discuss the general idea of saddle-point methods in relation to convex surrogates.

@@

\paragraph{Acknowledgements.}
Thanks to Cameron Freer, Simon Lacoste-Julien, Martin Jaggi, Percy Liang, Arun Chaganty, and Sida Wang 
for helpful discussions. Thanks also to the anonymous reviewer for suggesting improvements 
to the paper. JS was supported by the Hertz Foundation. JHH was supported by the U.S. Government under FA9550-11-C-0028 and awarded by the Department of Defense, Air Force Office of Scientific Research, National Defense Science and Engineering Graduate (NDSEG) Fellowship, 32 CFR 168a.
